--- 
title: "Dataset guide"
author: "Joyce Robbins"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
---

```{r}
knitr::opts_chunk$set(message = FALSE, warning = FALSE, cache = TRUE)
```


# R Packages

## Exploring data in packages:

Install **datacat**:

```{r, eval = FALSE}
remotes::install("jtr13/datacat")
```

View information with:

```{r, eval = FALSE}
library(datacat)
get_dataset_info("ggplot2") %>% View()
```

## List of packages with data

### [`alr4`](https://CRAN.R-project.org/package=alr4)


**Applied Linear Regression, 4th ed.**

Datasets to Accompany S. Weisberg, *Applied Linear Regression, 4th edition* (2014). Many data files in this package are included in the **alr3** package as well, so only one of them should be used.


```{r}
library(datacat)
get_dataset_info("alr4") %>% DT::datatable()
```

### [`dslabs`](https://CRAN.R-project.org/package=dslabs)

**Data Science Labs**

*Rafael A. Irizarry, Amy Gill*

Datasets and functions that can be used for data analysis practice, homework and projects in data science courses and workshops. 26 datasets are available for case studies in data visualization, statistical inference, modeling, linear regression, data wrangling and machine learning.

```{r}
get_dataset_info("dslabs") %>% DT::datatable()
```


### [`MASS`](https://CRAN.R-project.org/package=MASS)

**Modern Appplied Statistics with S**

Functions and datasets to support Venables and Ripley, *Modern Applied Statistics with S* (4th edition, 2002).

```{r, results='asis'}
get_dataset_info("MASS") %>% DT::datatable()
```

